Country-Level Impact of Education on Entrepreneurship

### 2014-12-11 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

Rather than trying to trace cultural features at large, we intend to focus on one key cultural institution, that is the education system. Indeed, like many in the education literature tend to assert, we believe that school personnel have an affect on student self-confidence [@Scott1996]. Now in entrepreneurship literature, "self-confidence was found to depend almost exclusively on the individual features of the respective person and his or her integration in social networks " [@OECD2009].

>>>>

Rather than trying to trace cultural features at large, as we mentioned earlier, we intend to focus specifically on one key cultural institution, that is the education system. Indeed, like many in the education literature tend to assert, we believe that school personnel have an affect on students' self-confidence [@Scott1996]. Now in entrepreneurship literature, "self-confidence was found to depend almost exclusively on the individual features of the respective person and his or her integration in social networks " [@OECD2009].
